Deep Reinforcement Learning for Conservation Decisions

### 2021-05-07 manuscript/manuscript.Rmd
setup for wildfire example

@@

@@

>>>>

## Unsolved environments: Wildfires and other examples

One feature that most distinguishes RL from other approaches to decision theory (such as optimal control) is it's flexibility or ambition.
While optimal control approaches typically require extensive simplifying assumptions such as discrete states or actions, deterministic dynamics or short time horizons, RL is scoped more ambitiously.
Large, complex problems are still immensely challenging to RL, and existing RL approaches will frequently struggle to solve problems that can already be solved much more efficiently by other means.
Nevertheless, deep RL approaches using neural network architectures have proven successful on problems that no amount of computational power would put into reach of purely conventional methods.
Our previous examples have focused on relatively simple examples that can also be addressed at least approximately by conventional methods, and also permit RL-based solutions to be found relatively efficiently on commodity hardware.
To better illustrate the generality of RL approach and more typical complexity of conservation problems, we now introduce a third example for which we have not yet found an effective policy using RL or classical methods.

@@

In this paper, we have highlighted the great potential that Reinforcement Learning, and in particular, of model-free *deep* RL has for helping confront challenging ecological and environmental management issues in a changing world.

@@

- Model Free

- Results

- Technical Caveats

- Social Caveats

- Way Forward
  Open Competition & Collaboration
  Leaderboards
